Generalized Tractability

### 2023-04-02 GeneralizedTractability_230310.tex
Updates from Overleaf
Fred's Home Computer

For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $j(\infty,\vp)$, so
\[
j\le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge j(\infty,\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{gather*}
 K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{j,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,\vp) \\
 \frac{1}{T (\lambda_{j,d}^{-1},1,\tau \vp)} \le
\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(j-1)^\tau}\qquad \forall j \ge j(\infty,\vp)
\end{gather*}
Summing both sides of this last inequality for $j$ from $j(\infty,\vp) \ge 1$ to $\inft$ yields 
\begin{align*}
\sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
& \le  \sup_{d\in\naturals} \frac{1}{T (\lambda_{1,d}^{-1},1, \tau \vp)} + K_{\vp,\tau}\, C_{\vp}^\tau
\sum_{j=2}^\infty \frac{1}{(j-1)^\tau} \\
& \le\frac{1}{T (\lambda_{\max}^{-1},1, \tau \vp)} +  K_{\vp,\tau}\, C_{\vp}^\tau
\zeta (\tau)  < \infty,
\end{align*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

@@

\begin{proof}
    \textbf{Sufficient Condition:}\\
Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$. By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the complexity has an upper bound of
\begin{equation*}
	 \comp(\varepsilon,d) \le 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
\end{equation*}

Let $J(\vp,d): = \lceil L_{\vp}\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]
        \\
       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L_{\vp}\, T(0,d,\vp) + S_{\vp}\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
       & \le 1+L_{\vp}\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
       & \le 1+L_{\vp}\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
       & \le 1+L_{\vp}\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
       & \le C_{2}(2\vp) \,T(\varepsilon^{-1},d,2\vp)
\end{align*}
for some suitably chosen $C_{2}(2\vp)>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\

>>>>

For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $j(\infty,\vp)$, so
\[
j\le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge j(\infty,\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{gather*}
 K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{j,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,\vp) \\
 \frac{1}{T (\lambda_{j,d}^{-1},1,\tau \vp)} \le
\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(j-1)^\tau}\qquad \forall j \ge j(\infty,\vp)
\end{gather*}
Summing both sides of this last inequality for $j$ from $j(\infty,\vp) \ge 1$ to $\infty$ yields 
\begin{align*}
\sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
& \le  \sup_{d\in\naturals} \frac{1}{T (\lambda_{1,d}^{-1},1, \tau \vp)} + K_{\vp,\tau}\, C_{\vp}^\tau
\sum_{j=2}^\infty \frac{1}{(j-1)^\tau} \\
& \le\frac{1}{T (\lambda_{\max}^{-1},1, \tau \vp)} +  K_{\vp,\tau}\, C_{\vp}^\tau
\zeta (\tau)  < \infty,
\end{align*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

@@

\begin{proof}
    \textbf{Sufficient Condition:}\\
Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$. By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the complexity has an upper bound of
\begin{equation*}
	 \comp(\varepsilon,d) \le  T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
\end{equation*}

Let $J(\vp,d): = \lceil L_{\vp}\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
\begin{align*}
       \comp(\varepsilon,d)
       & = T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
       & \le T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]
        \\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right] \\
       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},d,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},d,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
       & \le \frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},d,\vp)}  T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp)
\end{align*}
It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\
